---
title: "Weight of Fish"
author: "Juan Moreno"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
fish<-read.csv(file="Fish.csv")
```

# Predicting Fish Weight


## Perch
```{r}
Perch <- filter(fish, Species== "Perch" )
Perch <- select(Perch, -Species)
```


### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
With the help of the graph above I can say the best   regressor model is Height and Width which can help us   predict the weight of a fish.  


## Pike
```{r}
Pike <- filter(fish, Species== "Pike" )
Pike <- select(Pike, -Species)
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
According to the graph the best model for Pike are Length 1-3 with Height and Width seeing as its near the top of the graph.  

## Roach
```{r}
Roach <- filter(fish, Species== "Roach" )
Roach <- select(Roach, -Species)
```

### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
Looking at the graph I can confidently say that the best two regressor model are Length3 and width. 

## Final Summary Statements
From looking at all three graphs about the different fishes I can see that to predict a weight of a fish will require different   regressor, since each fish cant be predicted the same, a example being a Perch and a Smelt since both are a diffrent species   that comes in completely diffrent sizes.  